Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-15 paper/paper.qmd
results table 2

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
```

@@

Data from Study 1 were used to show the relative amount of belief in free will 
of the average Taiwanese real estate agents and how much are they satisfied with
their job across two times within 6 months with the same sample.
We extracted the responses from the survey and extracted the responses to the 
questions : "From the scale of 0 to 10, How much do you agree with this 
statement: I have free will"and "From the scale of 0 to 10, How much do you 
agree with this statement: I am satisfied with my job" at Time one and two.
In Table 1, there are three values on a scale of 0 to 10 compared : 
(1) Job Satisfaction T1, (2) Job Satisfaction T2, and (3) Belief in Free Will 
which is only measured once since beliefs rarely vary on a relatively short time
span.
The rows would be the mean and standard deviation calculated using R.
Looking at Table 1, we immediately notice that the mean score of Job 
satisfaction barely vary from the first and second time (5.64 and 5.74 
respectively) and that the average level of belief of free will would be 3.99. 
In addition,the standard deviation of the three values seem reasonable.
In analyzing Table 1, we can recognize that the slight increase in job
satisfaction still within the standard deviation.

```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

@@

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_II <- data.frame(
  Job_satisfaction = c(5.29, 1.22),
  Belief_free_will = c(5.28, 0.84)
)

@@

print(Table_II)
```
```{r}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)

@@

```
Talk way more about it.

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(knitr)
```

@@

Data from Study 1 were used to show the relative amount of belief in free will 
of the average Taiwanese real estate agents and how much are they satisfied with
their job across two times within three months with the same sample.
We extracted the responses from the survey and extracted the responses to the 
questions : "From the scale of 0 to 10, How much do you agree with this 
statement: I have free will"and "From the scale of 0 to 10, How much do you 
agree with this statement: I am satisfied with my job" at Time one and two.
In Table 1, there are three values on a scale of 0 to 10 compared : 
(1) Job Satisfaction T1, (2) Job Satisfaction T2, and (3) Belief in Free Will.
The rows would be the mean and standard deviation calculated using R.
Looking at Table 1, we immediately notice that the mean score of Job 
satisfaction barely vary from the first and second time (5.64 and 5.74 
respectively) and that the average level of belief of free will would be 3.99. 
In addition,the standard deviation of the three values seem reasonable.
While analyzing Table 1, we can recognize that the slight increase in job
satisfaction still largely within the standard deviation which confirms the 
accuracy of the measurement that barely varies over the time.

Table 1 : Mean and standard deviation of belief in free will and 
job satisfaction within the Taiwanese real estate agency.
```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_I <- data.frame(
  Job_satisfaction_T1 = c(5.64, 1.18),
  Job_satisfaction_T2 = c(5.74, 0.99),
  Belief_free_will = c(3.99, 0.49)
)

@@

Moving to the United States, Study 2 ,conducted in 2017, asked workers available 
on MTurk, a professional network spanning multiple professions the same 
questions as in Study 1 :  "From the scale of 0 to 10, How much do you agree 
with this statement: I have free will"and "From the scale of 0 to 10, How much 
do you agree with this statement: I am satisfied with my job". The respondents'
answers were extracted and had their average and standard deviation as given 
in Table 2. This table compares two values on a scale of 0 to 10  : 
(1) Job Satisfaction T1 (2) Belief in Free Will. The rows would be the mean and
standard deviation calculated using R. Looking at Table 1, we see  that the mean
score of Job satisfaction is 5.29 and that the average level of belief of free 
will would be 5.28. The standard deviation of the three values seem reasonable.

Table 2 : Mean and standard deviation of belief in free will and job
satisfaction within Amazon Mechanical Turk American Workers.
```{r}
knitr::opts_chunk$set(echo = FALSE)
Table_II <- data.frame(
  Job_satisfaction = c(5.29, 1.22),
  Belief_free_will = c(5.28, 0.84)
)

@@

print(Table_II)
```

Graph 1 : Bar Chart comparing the belief in free will and job
satisfaction Mehanical Turk American Workers.

```{r}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)

@@
